---
title: 'Data Analysis Project - STAT 420 - Group Project'
author: "Luma Vasiljevic(lumav2), Sushanta Panda(panda5)"
date: 
output:
  html_document:
    theme: flatly
    toc: yes
    fig_width: 10
    fig_height: 5
  pdf_document:
    toc: yes
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
options(scipen = 1, digits = 4, width = 80)
library(knitr)
opts_chunk$set(cache = TRUE, autodep = TRUE)
```

# Introduction


###Description of the dataset:
Forced Expiratory Volume (FEV) is an index of pulmonary function that measures the volume of the air expelled after one second of constant effort. The data contains the determinations of FEB on 654 children ages 6 – 22 who are seen in childhood respiratory disease study in 1980 in East Boston, Massachusetts. The data are part of a larger study to follow the change in pulmonary function over time in children.

#####**Dataset Link: **
http://www.statsci.org/data/general/fev.html

#####**Variables in the Dataset:**

```{r include=FALSE}
Variable = data.frame(
  VariableName = c("ID","Age", "Height", "Sex", "Smoker", "FEV"),
  Category = c("Numeric","Numeric", "Numeric", "Categorical", "Categorical", "Numeric"),
  Description = c("Uniquely Identified Row","Age of the child", "Height of the child in inches", "Sex of the child ", "Whether the child is a non-smoker or current smoker", "FEV of the child in litres")
)
```


```{r echo=FALSE}
library(knitr)
kable(Variable, format = "pandoc",padding = 2)
```

#####**Background information of the dataset:**

The data contains the determinations of FEB on 654 children ages 6 – 22 who are seen in childhood respiratory disease study in 1980 in East Boston, Massachusetts. The data are part of a larger study to follow the change in pulmonary function over time in children

Note: No citation required for this source (http://www.statsci.org/data/general/fev.html)


###Interest in dataset hope to explore:
This dataset has chosen by us because of personal interests, whether we can predict the child’s FEV with the help of the available predictor, rather going for a Pulmonary Function Test, which will identify any pulmonary disease of a child. And secondly, to do statistical analysis on what are the predictors responsible to increase / decrease the pulmonary function of the child and try to find answer on these lines.

###Why are we creating a model of this Data:
In order to **predict the child's Forced Exporatory Volume (FEV)** based on the Child's Age, Height, Sex and whether the child is a smoker or not. This will help for kick-start the treatment of the child based on the FEV reading, rather going throgh the Pulmonary Function test.


###Goal of the Model:
The goal of the model is to predict the child's FEV with minimal error with the data available with us. We will be going throgh different statiscal analysis and methods to minimize the errors

