---
title: "Interactions"
author: "Sushanta Panda"
date: "6/29/2019"
output: html_document
---

```{r}
data = read.table("https://archive.ics.uci.edu/ml/machine-learning-databases/auto-mpg/auto-mpg.data",
                  quote = "\"",
                  comment.char = "",
                  stringsAsFactors = FALSE)
#Change the column name of the data set autompg
colnames(data) = c("mpg","cyl","disp","hp","wt","acc","year","origin","name")
#remove missing data stored as "?"
data = subset(data,data$hp != "?")
#remove the plymouth, as it causes issues
data = subset(data,data$name != "plymouth reliant")
#Assign the rowname, based on the engine, year and name
rownames(data) = paste(data$cyl,"cylinder",data$year,data$name)
#remove the variable for the name
data = subset(data,select = c("mpg","cyl","disp","hp","wt","acc","year","origin"))
#Change the horsepower from character to name
data$hp = as.numeric(data$hp)
#Creata a dummy variable for foreign vs domestic cars, domestic = 1
data$domestic = as.numeric(data$origin == 1)
#remove the 3 and 5 cylinder cars, as they arr very rare
data = data[data$cyl != 5,]
data = data[data$cyl != 3,]
#the following line would verify the remaining cylinder possibilities are 4,6,8
#unique(data$cyl)
#change cyl to a factor variable
data$cyl = as.factor(data$cyl) 
```

```{r}
str(data)
```

$$
Y = \beta_0 + \beta_1 x_1 + \beta_2 x_2 + \epsilon
$$

where

- $Y$ is `mpg`, the fuel efficieny in miles per gallon 
- $x_1$ is `disp`, the displacement in cubic inches
- $x_2$ is `domestic` as described above, is a dummy variable

$$
x_2 = 
  \begin{cases}
  1 & \text{Domestic} \\
  0 & \text{Foreign}\\  
  \end{cases}
$$


```{r}
mpg_disp_add = lm(mpg~disp+domestic,data=data)
int_for = summary(mpg_disp_add)$coefficient[1,1]
int_dom = summary(mpg_disp_add)$coefficient[1,1] + summary(mpg_disp_add)$coefficient[3,1]

slope_for = summary(mpg_disp_add)$coefficient[2,1]
slope_dom = summary(mpg_disp_add)$coefficient[2,1]

plot(mpg~disp, data = data,col = domestic + 1,pch = domestic + 1)
abline(int_for,slope_for,lwd=3,col=2,lty=1)
abline(int_dom,slope_dom,lwd=3,col=1,lty=2)
legend("topright",legend=c("Foreign","Domestic"),col=c(1,2),pch=c(1,2))
```


$$
Y_i = \beta_0 + \beta_1 x_1 + \beta_2 x_2 + \beta_3 x_1 x_2 + \epsilon
$$

For domestic cars, that is $x_2 = 1$, we have 
$$
Y_i = (\beta_0 + \beta_2) + (\beta_1 +\beta_3 ) x_1 + \epsilon
$$

For foreign cars, that is $x_2 = 0$, we have 
$$
Y_i = \beta_0 + \beta_1 x_1 + \epsilon
$$

These two models have both different slopes and interceps

- $\beta_0$ is the average `mpg` for foreign cars when the `disp` is **0**
- $\beta_1$ is the change in average `mpg`, when the `disp` is increased by 1, for **foreign** cars 
- $\beta_0 + \beta_2$ is average `mpg` for domestic cars when the `disp` is **0**
- $\beta_1 + \beta_3$ is the change in average `mpg`, when the `disp` is increased by 1, for **domestic** cars 


```{r}
mpg_disp_inter = lm(mpg~disp + domestic + disp:domestic,data=data)
int_for = summary(mpg_disp_inter)$coefficient[1,1]
int_dom = summary(mpg_disp_inter)$coefficient[1,1]+summary(mpg_disp_inter)$coefficient[3,1]

slope_for = summary(mpg_disp_inter)$coefficient[2,1]
slope_dom = summary(mpg_disp_inter)$coefficient[2,1] + summary(mpg_disp_inter)$coefficient[4,1]

plot(mpg~disp,data=data,col=domestic+1,pch=domestic+1)
abline(int_for,slope_for,lwd=2,col=1,lty=1)
abline(int_dom,slope_dom,lwd=2,col=2,lty=2)
legend("topright",legend=c("Foreign","Domestic"),col=c(1,2),pch=c(1,2))
```

#Numeric-Numeric Interaction

$$
Y_i = \beta_0 + \beta_1 x_1 + \beta_2 x_2 + \beta_3 x_1 x_2 + \epsilon
$$

where

- $Y$ is `mpg`, the fuel efficient in miles per gallon
- $x_1$ is the `disp`, the displacement in cubic inches
- $x_2$ is the `hp`, the horsepower, in foot-pound per square

$$
Y_i = \beta_0 + (\beta_1 + \beta_3 x_2) x_1 + \beta_2 x_2 + \epsilon
$$

```{r}
mpg_disp_add_hp = lm(mpg~disp+hp,data=data)
mpg_disp_int_hp = lm(mpg~disp*hp,data=data)

summary(mpg_disp_int_hp)
```

$$
H_0: \beta_3 = 0, H_1 : \beta_3 \neq 0
$$
```{r}
anova(mpg_disp_add_hp,mpg_disp_int_hp)
```

$$
Y_i = \beta_0 + \beta_1 x_1 + \beta_2 v_2 + \beta_3 v_3 + \epsilon
$$
$$
v1 = 
 \begin{cases}
 1 & \text{4 Cylinder} \\
 0 & \text{Not a 4 Cylinder}
 \end{cases}
$$

$$
v2 = 
 \begin{cases}
 1 & \text{6 Cylinder} \\
 0 & \text{Not a 6 Cylinder}
 \end{cases}
$$

$$
v3 = 
 \begin{cases}
 1 & \text{8 Cylinder} \\
 0 & \text{Not a 8 Cylinder}
 \end{cases}
$$
For a 4 Cylinder Engine, $v_2$ and $v_3$ will be **0**
$$
Y_i = \beta_0 + \beta_1 x_1 + \epsilon
$$

For a 6 Cylinder Engine, $v_2$ = 1 and $v_3$ = **0**
$$
Y_i = (\beta_0 + \beta_2) + \beta_1 x_1 + \epsilon
$$

For a 8 Cylinder Engine, $v_2$ = 0 and $v_3$ = **1**
$$
Y_i = (\beta_0 + \beta_3) + \beta_1 x_1 + \epsilon
$$


```{r}
mpg_disp = lm(mpg~disp,data=data)
mpg_disp_add_cyl = lm(mpg~disp+cyl,data=data)
int_4cyl = summary(mpg_disp_add_cyl)$coefficient[1,1]
int_6cyl = summary(mpg_disp_add_cyl)$coefficient[1,1] + summary(mpg_disp_add_cyl)$coefficient[3,1]
int_8cyl = summary(mpg_disp_add_cyl)$coefficient[1,1]+ summary(mpg_disp_add_cyl)$coefficient[4,1]

slope_all_cyl = summary(mpg_disp_add_cyl)$coefficient[2,1]

plot_colours = c("Darkorange","Darkgrey","Dodgerblue")
plot(mpg~disp,data=data,col=plot_colours[cyl],pch=as.numeric(cyl))
abline(mpg_disp,lwd=1,col="green",lty=8)

abline(int_4cyl,slope_all_cyl,lwd=2,col=plot_colours[1],lty=1)
abline(int_6cyl,slope_all_cyl,lwd=2,col=plot_colours[2],lty=2)
abline(int_8cyl,slope_all_cyl,lwd=2,col=plot_colours[3],lty=3)

legend("topright",legend=c("4 Cyliner","6 Cyliner","8 Cyliner"),col=plot_colours,pch=c(1,2,3))
```

Below is the interaction model
$$
Y_i = \beta_0 + \beta_1 x + \beta_2 v_2 + \beta_3 v_3 + \gamma_2 x v_2 + \gamma_3 x v_3 + \epsilon
$$
For a 4 Cylinder Engine
$$
Y_i = \beta_0 + \beta_1 x + \epsilon
$$
For a 6 Cylinder Engine
$$
Y_i = (\beta_0 + \beta_2) + (\beta_1 + \gamma_2) x + \epsilon
$$
For a 8 Cylinder Engine
$$
Y_i = (\beta_0 + \beta_3) + (\beta_1 + \gamma_3) x + \epsilon
$$

```{r}
mpg_disp_int_cyl = lm(mpg~disp*cyl,data=data)
int_4cyl = summary(mpg_disp_int_cyl)$coefficient[1,1]
int_6cyl = summary(mpg_disp_int_cyl)$coefficient[1,1] + summary(mpg_disp_int_cyl)$coefficient[3,1]
int_8cyl = summary(mpg_disp_int_cyl)$coefficient[1,1] + summary(mpg_disp_int_cyl)$coefficient[4,1]

slope_4cyl = summary(mpg_disp_int_cyl)$coefficient[2,1]
slope_6cyl = summary(mpg_disp_int_cyl)$coefficient[2,1] + summary(mpg_disp_int_cyl)$coefficient[5,1]
slope_8cyl = summary(mpg_disp_int_cyl)$coefficient[2,1] + summary(mpg_disp_int_cyl)$coefficient[6,1]

plot (mpg~disp,data=data,col=plot_colours[cyl],pch=as.numeric(cyl))
abline(int_4cyl,slope_4cyl,lwd=2,col=plot_colours[1],pch=1,lty=1)
abline(int_6cyl,slope_6cyl,lwd=2,col=plot_colours[2],pch=2,lty=2)
abline(int_8cyl,slope_8cyl,lwd=2,col=plot_colours[3],pch=3,lty=3)
legend("topright",legend=c("4 Cyliner","6 Cyliner","8 Cyliner"),col=plot_colours,pch=c(1,2,3))
```

Now, do the F Test between the Additive Model and Interaction Model, below are the 2 models

$$
H_0 : \gamma_2 = \gamma_3 = 0
$$


Below is the Additive Model
$$
Y_i = \beta_0 + \beta_1 x_1 + \beta_2 v_2 + \beta_3 v_3 + \epsilon
$$

Below is the Interaction Model
$$
Y_i = \beta_0 + \beta_1 x + \beta_2 v_2 + \beta_3 v_3 + \gamma_2 x v_2 + \gamma_2 x v_3 + \epsilon
$$


```{r}
anova(mpg_disp_add_cyl,mpg_disp_int_cyl)
```

##Parameterization

$$
Y_i = \beta_0 + \beta_1 x + \beta_2 v2 + \beta_3 v3 + \gamma_2 x v2 + \gamma_3 x v3 + \epsilon
$$

$$
Y_i = \mu_1 v_1 + \mu_2 v_2 + \mu_3 v_3 + \beta_1 x v_1 + \beta_2 x v_2 + \beta_3 x v_3 + \epsilon
$$


```{r}
lm(mpg~disp*cyl,data=data)
lm(mpg~disp+cyl+disp:cyl,data=data)
lm(mpg~0+cyl+cyl:disp,data=data)
lm(mpg~0+cyl+cyl*disp,data=data)
```

## Larger Models

$$
Y_i = \beta_0 + \beta_1 x_1 + \beta_2 x_2 + \beta_3 x_3 + \beta_4 x_1 x_2 + \beta_5 x_1 x_3 + \beta_6 x_2 x_3 + \beta_7 x_1 x_2 x_3 + \epsilon
$$


```{r}
two_way_int_model1 = lm(mpg~disp * hp + disp * domestic + domestic * hp ,data=data)
large_model1 = lm(mpg~disp * hp * domestic,data=data)
large_model2 = lm(mpg~disp+hp+cyl+disp:hp+disp:cyl+disp:hp:cyl,data=data)
```

$$
H_0 : \beta_7 = 0
$$

```{r}
anova(two_way_int_model1,large_model1)
```