---
title: "Seat Position - Corelation"
author: "Sushanta Panda"
date: "7/12/2019"
output: html_document
---

#Corelation Plot of the Seat Position Data from the Faraway package

### Plot the Pair Plot
```{r fig.height=4, fig.width=4}
pairs(seatpos,col = "dodgerblue")
```
##See the Corelation Coefficient
```{r}
round(cor(seatpos),2)
```

##Model for all model Predictors
```{r}
hip_model = lm(hipcenter~., data = seatpos)
summary(hip_model)
```

###Varience Inflation Factor (VIF)

```{r}
ht_shoes_model = lm(HtShoes~.-hipcenter, data = seatpos)
summary(ht_shoes_model)$r.squared
```

This means the `HtShoes` is well explained by the other predictor in the model. Especially if we see the `pairs` plot, it clearly explained that `Ht` and `HtShoes` predictor is having a linear relationship.

```{r}
car::vif(hip_model)
```

From the above, it sees that `HtShoes` and `Ht` have the high variation inflation factor (vif)

Let's add some noise to the hipcenter and see what's the impact of the varience of the parameter
```{r}
set.seed(1337)
noise = rnorm(n = nrow(seatpos), mean = 0, sd = 5)
hip_model_noise = lm(hipcenter+noise~., data = seatpos)
```



```{r}
coef(hip_model)
coef(hip_model_noise)
```

From the above it see that the by adding a little noise to the hip center data, also it seems the the parameter sign have reversed for the parameter `Ht`

Let's plot the fitted value of the model which are predicted from the acutal versis actual + noise
```{r}
plot(fitted(hip_model),fitted(hip_model_noise),col = "dodgerblue", pch = 1, cex = 1, xlab = "Predicted, without Noise", ylab = "Predicted, with Noise")
abline(0, 1, col = "darkorange",lwd = 2)
```